Estimating demographic bias on tests of children's early vocabulary

### 2022-02-24 paper/cogsci_word.Rmd
added funding statement

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

@@

[Redacted for anonymous review.]
<!--We thank members of the Language and Cognition lab for their feedback.-->

>>>>

output: word_document
#final-submission: \cogscifinalcopy
---

@@

[Redacted for anonymous review.]
<!--We thank members of the Language and Cognition lab for their feedback.
This research was supported by the Stanford Maternal and Child Health Research Institute.  
-->
